Comparing order of acquisition cross-linguistically

### 2018-12-17 languages.Rmd
new sampling mechanisms

unilemmas <- (data_by_lang[[3]] %>% #English (I should recode this to be more explcit)
    filter(!is.na(uni_lemma)) %>%
    trim_all_unilemma() %>%
    select(uni_lemma) %>%
    #(uni_lemma))$uni_lemma
    unique())$uni_lemma

@@

vocab <- names(matrix_sim[word_0, ])
#Now generate a sequence based on the first word

sim_learning <- function() {
  seq_gen <- function(word_t0, sequence_t0) {

@@

>>>>

unilemmas <- (data_by_lang[[3]] %>% #I use English data to derive unilemmas, see above (but I should recode this to be cleaner)
    filter(!is.na(uni_lemma)) %>%
    trim_all_unilemma() %>%
    select(uni_lemma) %>%
    #(uni_lemma))$uni_lemma
    unique())$uni_lemma

@@

vocab <- names(matrix_sim[word_0, ])

#Sampling via

## Sampling via comparing similarity to last known words

lastWord <- function() {
  seq_gen <- function(word_t0, sequence_t0) {

@@

## Sampling via averaging to similarity to all known

allWords <- function() {
  seq_gen <- function(sequence_t0) {

    if (length(sequence_t0) == length(matrix_sim[sequence_t0[1], ])) {
      return (sequence_t0)
    } else {

      ave_sim <- function(candidate) {
        all <- matrix_sim[candidate, ] #Similarity values to all words 
        values <- all[names(all) %in% sequence_t0] # Similarity values to known words only
        return(data.frame(word = candidate, value = mean(values)))
      }

      #all words
      all <- names(matrix_sim[sequence_t0[1], ])
      candidates <- setdiff(all, sequence_t0)
      list_sim  <- map(candidates, ave_sim) %>%
        bind_rows()
      max_value <- list_sim[which.max(list_sim$value),]
      word_t1 <- max_value$word[1]
      sequence_t1 <- c(sequence_t0, word_t1)

      return(seq_gen(sequence_t1))
    }
  }
  word_0 <- sample(vocab, 1) # this is the only random compoenent
  sequence_0 <- c(word_0)
  return(seq_gen(sequence_0))
}

```{r}
